### 2016-10-06 robust-software.tex

\item
Cite http://hmmer.org/ as an example of scientific software done right.

\item
Suggest that people put all the checking and validation up front,
so that if the program is going to crash it does so right away
(rather than in the middle of the night after 18 hours of runtime).

\item
Should we tell people to create several single-purpose tools
rather than One Script to Rule Them All?

\item
Should we tone down the ``tremor of fear'' remark?

\item
``Keep in mind that if a parameter can be adjusted,
users will want to be able to turn off the feature entirely to have a baseline comparison.''
What's the relationship here between parameter and feature?

@@

\fixme{GW}{Write non-technical paragraph for the general public.}

@@

Typically, scientific software is developed and used by a single person,
usually a graduate student or postdoc, and produces intended results in their
hands~\cite{prins2015}. 
But what happens
when someone else wants to use their software? Everyone with
a few years of experience feels a tremor of fear when told to use
a graduated student's code to analyze their data.
Often, that software will be undocumented and work in unexpected
ways (if it works at all).  It will often rely on nonexistent paths or resources,
be tuned for a single dataset,
or simply be an older version than was used in published papers.
The new user is then faced with two unpalatable options:
hack the existing code to make it work, or start over. Being unable to
replicate results is so common that one publication refers to it as "a rite of
passage"~\cite{baker2016}.

>>>>

@@

Many researchers have found out the hard way that there's a world of difference
between ``works for me on my machine'' and ``works for other people on theirs''.
Many common challenges can be avoided by following a few simple rules; doing so
not only accelerates research, but also improves reproducibility.

@@

Typically, scientific software is developed and used by a single person,
usually a graduate student or postdoc, and produces intended results in their
hands~\cite{prins2015}. 
But what happens
when someone else wants to use their software? Everyone with
a few years of experience feels a bit nervous when told to use
a graduated student's code to analyze their data.
Often, that software will be undocumented and work in unexpected
ways (if it works at all).  It will often rely on nonexistent paths or resources,
be tuned for a single dataset,
or simply be an older version than was used in published papers.
The new user is then faced with two unpalatable options:
hack the existing code to make it work, or start over. Being unable to
replicate results is so common that one publication refers to it as "a rite of
passage"~\cite{baker2016}.
